Distances between histograms

### 2015-10-28 tables/tabNormNull.tex
terminado tudo menos a parte com as leis de potencia

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 2 & 3 & 5 \\\hline
5.0 & 0.050 & 1.36 & 1 & 1 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 normal distributions with $\mu=0$ and $\sigma=1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 normal distributions with $\mu=3$ and $\sigma=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7015$ and $\sigma(c_1')=0.2315$,
 $\mu(c_2')=0.7176$ and $\sigma(c_2')=0.2658$,
 $\mu(c_3')=0.7348$ and $\sigma(c_3')=0.2527$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 6 & 2 & 3 \\\hline
5.0 & 0.050 & 1.36 & 3 & 1 & 0 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 0 \\\hline
1.0 & 0.010 & 1.63 & 0 & 1 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 1 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 normal distributions with $\mu=0$ and $\sigma=1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 normal distributions with $\mu=3$ and $\sigma=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=6$ and $\sigma=3$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7243$ and $\sigma(c_1')=0.2479$,
 $\mu(c_2')=0.6959$ and $\sigma(c_2')=0.2627$,
 $\mu(c_3')=0.7307$ and $\sigma(c_3')=0.2259$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabUniformNull.tex
terminado tudo menos a parte com as leis de potencia

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 7 & 6 & 6 \\\hline
5.0 & 0.050 & 1.36 & 4 & 1 & 2 \\\hline
2.5 & 0.025 & 1.48 & 1 & 1 & 2 \\\hline
1.0 & 0.010 & 1.63 & 1 & 1 & 1 \\\hline
0.5 & 0.005 & 1.73 & 1 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 1 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 uniform distributions within $[0,1)$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 uniform distributions within $[2,6)$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7415$ and $\sigma(c_1')=0.2904$,
 $\mu(c_2')=0.7954$ and $\sigma(c_2')=0.2462$,
 $\mu(c_3')=0.7934$ and $\sigma(c_3')=0.2981$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 4 & 5 & 5 \\\hline
5.0 & 0.050 & 1.36 & 2 & 0 & 1 \\\hline
2.5 & 0.025 & 1.48 & 1 & 0 & 0 \\\hline
1.0 & 0.010 & 1.63 & 1 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 1 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 1 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 uniform distributions within $[0,1)$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 uniform distributions within $[2,6)$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 normal distributions with $\mu=4$ and $\sigma=10$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.7350$ and $\sigma(c_1')=0.2556$,
 $\mu(c_2')=0.7314$ and $\sigma(c_2')=0.2435$,
 $\mu(c_3')=0.6965$ and $\sigma(c_3')=0.2489$ .
}
\end{center}
\end{table}

### 2015-10-28 tables/tabWeibullNull.tex
terminado tudo menos a parte com as leis de potencia

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 4 & 2 & 7 \\\hline
5.0 & 0.050 & 1.36 & 0 & 2 & 1 & 3 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 1 & 1 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 0 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 0 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=0.1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.0635$ and $\sigma(c_1')=0.0388$,
 $\mu(c_2')=0.7178$ and $\sigma(c_2')=0.2499$,
 $\mu(c_3')=0.7167$ and $\sigma(c_3')=0.2379$ .
 $\mu(c_4')=0.7073$ and $\sigma(c_4')=0.2583$ .
}
\end{center}
\end{table}

>>>>

\begin{table}[h!]
\begin{center}
\begin{tabular}{| l | c | c | c | c | c | c |}\hline
$\alpha N_c$ & $\alpha$ & $c(\alpha)$ & $|C_1'(\alpha)|$ & $|C_2'(\alpha)|$ & $|C_3'(\alpha)|$ & $|C_4'(\alpha)|$ \\\hline
10.0 & 0.100 & 1.22 & 0 & 5 & 0 & 3 \\\hline
5.0 & 0.050 & 1.36 & 0 & 2 & 0 & 2 \\\hline
2.5 & 0.025 & 1.48 & 0 & 1 & 0 & 2 \\\hline
1.0 & 0.010 & 1.63 & 0 & 0 & 0 & 2 \\\hline
0.5 & 0.005 & 1.73 & 0 & 0 & 0 & 1 \\\hline
0.1 & 0.001 & 1.95 & 0 & 0 & 0 & 0 \\\hline
\end{tabular}
\caption{The theoretical maximum number $\alpha N_c$ of rejections
of the null hypothesis for critical values of $\alpha$.
The number of comparisons is $N_c=100$,
each with the sample size of $N_o=1000$ observations.
Each histogram have $N_b=30$ equally spaced bins.
The $N_o$ values of $c_1'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=0.1$.
The $N_o$ values of $c_2'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=2$.
The $N_o$ values of $c_3'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=4$.
Over all $N_c$ comparisons,
The $N_o$ values of $c_4'$ were calculated using simulations of
 1-parameter Weibull distributions with $a=6$.
Over all $N_c$ comparisons,
 $\mu(c_1')=0.0628$ and $\sigma(c_1')=0.0517$,
 $\mu(c_2')=0.7261$ and $\sigma(c_2')=0.2673$,
 $\mu(c_3')=0.6970$ and $\sigma(c_3')=0.2266$ .
 $\mu(c_4')=0.6708$ and $\sigma(c_4')=0.2451$ .
}
\end{center}
\end{table}
